\chapter*{Acknowledgement}

My gratitude goes to both of my supervising professors Eva Hornecker and Sven Bertel. Their expertise and counsel kept me on track and gave me helpful impulses. 
\\
Further, I want to thank Diethard Walter and Karin Sietz from the Museum für Ur- und Frühgeschichte for partnering with us and facilitating this work. 
\\
Special thanks goes to Felix Kistler from Universität Augsburg. The FUBI framework is playing an important role in the implementations of the software components of the system. 

I want to thank the staff at the faculty of Media at Bauhaus-Universität Weimar. Especially the staff from the Chairs of Human-Computer Interaction and Usability were always there to lend a hand or discuss certain issues. Thus, I want to thank Michaela Honauer, Patrick Tobias Fischer, Maximilian Schirmer and Stefanie Wetzel.
\\
Next, I want to thank Stephan Beck and André Kunert from the Chair of Virtual Reality and Visualization Research for their generosity and their expertise. Moreover, I want to thank Stefan Lucks, Jakob Wenzel and Eik List for their backup during the writing process of my work. My special thanks go to Ursula Schmitt, Christin Oehmichen and Nadin Galser for their kind and administrative support.

I would like to thank Katharina Spiel for her revisions of this work and Daniela Elflein and Helga Schneider for their artistic advice and inspiration. Moreover, I have to thank my roommates Frederick Boulassel, Laurina Bleier, and Loreen Dalski for their patience with me and coping with my moods.



%Great thanks goes to my parents Annemarie and Joachim and my brothers Justus and Jan, who have supported me during the past two years, morally and financially.
%Furthermore, I would like to thank the owner of the Chair of Media Security professor Stefan Lucks, who has given me the opportunity to work in the
%ever-growing reasearch area of cryptography. I owe my gratitude to my advisor Christian Forler, who, with his constructive
%criticism and helpful remarks, helped guide this thesis to its proper destination. I also thank Christof Bräutigam, Ewan Fleischmann, Lars Harmsen,
%Alexander Kümmel, Eik List, Thomas Knapke, Michael Pannier und Michael Völske, for their interminable support during the time
%I spent working on this thesis, as well as Benno Stein for co-supervising it.
%
%
%\vfill
%
%\section*{Danksagung}
%
%Mein größter Dank geht an meine Eltern Annemarie und Joachim und meine Brüder Justus und Jan, die mich während der letzten zwei Jahre moralisch und finanziell unterstützt haben.
%Danken möchte ich dem Inhaber des Lehrstuhls für Mediensicherheit Professor Stefan Lucks, der mir die Möglichkeit gegeben hat, in dem
%stetig wachsenden Forschungsgebiet der Kryptographie zu arbeiten. Meinem Betreuer Christian Forler gehört Dank, denn mit seiner konstruktiven
%Kritik und seinen guten Anmerkungen hat er diese Arbeit zu einem guten Ziel geführt.
%Weiter danke ich Christof Bräutigam, Ewan Fleischmann, Lars Harmsen, Alexander Kümmel, Eik List, Thomas Knapke, Michael Pannier und Michael Völske, die mir
%während meiner Bearbeitungszeit stets mit Rat und Tat zur Seite standen sowie meinem Zweitbetreuer Professor Benno Stein.

